Eclipse Che for Fair and Easy Education

### 2019-06-12 che.tex
Minor removal and fixes

\begin{abstract}
Eclipse Che is a revolutionary cloud-based IDE, inheriting the approach of building cloud native software within a 
remote environment. 
Instead of developing on a local machine, a remote development-server is accessed via web-browser 
and the artifacts are compiled into docker-containers.

@@

As Cloud is a central element of modern IT-development, it is strange to see that it is not yet widely teached across 
universities in Germany \footnote{https://www.hochschulkompass.de/studium/studiengangsuche lists currently only 10 german universities with courses on cloud computing, about 30 courses on virtualization }.
There are courses to teach either classic virtualization or docker-basics, but the knowledge of full-stack cloud-platforms and cloud native development is sealed behind corporate doors and conference workshops.
Meanwhile,  the  annual  StackOverflow  developer-survey \cite{SO19} showed, that DevOps-engineers are not only 
among the most wanted and best paid jobs but also tend to be the happiest participants.  
Every student either wants to be happy or to be rich, making Cloud an interesting topic for their career.

@@

The last component is the Che-administration server. 
In the administration-server workspaces are orchestrated and monitored. 
The authorization is also done at the admin-server and not by every workspace.
The workspaces can be shipped onto multiple separate machines.
The runtimes do not necessarily need to be on the same machines as their workspace. 
Instead of the web-based IDE, a desktop IDE can be connected to the workspace. 
This is done by mounting the workspaces-filesystem in the desktop  IDE. 
This  will grant access to auto-completion and other features, but will miss Che specific helpers the web-IDE offers. 
Mounting remote file systems for development sounds lie an infinite source of problems.
This feature looks to be rather a proof of concept.

A single workspace can contain multiple projects, whereof every project will have its own runtime. 
Projects can either share a versioning control or be separated. 
You can build whole pods in a single workspace with the single containers being the sub-projects. 
You can also compose applications inside the workspace, meaning that the resulting 
container of a project can be the base-image of another project. 
A workspace can be shared among multiple users. 
Both will work on the same remote filesystem, altering files simultaneous. 
Due to changes being transmitted as HTTP-requests, the current implementation when working on the same file is a \textit{last write wins}-policy. 
For version 7 a multi-cursor file-editing will be provided, like it`s common in 
drive-documents. 
This is not to be mixed up with having multiple users work on the same project but on their own workspace. 
The code, and the workspace itself, can commonly be shared with any versioning tool such as Git.
It's mostly dependent on the team which kind of cooperation they prefer.

As  an  interesting  fact,  Eclipse  Che  is  developed  with Eclipse Che, proving that complex cloud development is possible. 
This so-called \textit{dogfooding} usually leads to a product which puts requirements over any a-priori design or foreign interests.  
Existing components will be enhanced if working with them becomes troublesome, leaving a clean and valuable core product.

@@

\subsection{Reproduction and Maintenance}
The University of Arizona showed \cite{CO16}, that about 50\% of software inspected was not able to build. 
Common reasons are missing, changed or faulty dependencies, leading to the common term of \textit{dependency hell} as well as unclear documentation. 
Experienced programmers are usually able to overcome these issues, given enough time. This continues to be an issue \cite{CL14}, and without a different approach probably always will be.

@@

This is one of the primary goals of the DevOps approach \cite{JA16}. 
The workspace can therefore form totally new ways of programming, such as IoT Applications \footnote{the Plugin Arktik for Eclipse offered IoT Development with Che. While Arktik is unsupported since February 2019, it proved that the concept worked.} or a full setup of micro-services \cite{IV18}, while being agile and reproducible.
\subsection{Sharing Results}
The topic \textit{docker for reproducible research} has already been promoted \cite{BO15} and successfully applied to complex topics \cite{ST16} such as machine learning. 
As Clark et al. \cite{CL14} have used code of several repositories provided from their university, most of the projects can be expected scientific or experimental, 50\% of the research results were not reproducible.

@@

The combination of a quick setup and the usability of every enhancement makes Che especially interesting to recruit troubleshooters into projects, which solve some of the very specialized tasks.  
With  the  artifacts  being  reproducible,  the  expert  can quickly inspect the subject and analyze problems.
With a finished workspace they can quickly start working. 
With their changes being also in docker, they will be visible and functional for the whole team.
Therefore,  the  hardest  common  problems  regarding \textit{quick help} are addressed and solved. 
As an additional minor benefit, it is easy to hibernate resources  using  Che  with  Kubernetes  or  Openshift.
The workspaces collect metrics like any other container and are therefore scalable on demand. 
The ability of down-scaling the development resources has a big impact on the overall 
workload. 
As a further example, the workspace could be shut down out of normal business-time. This attribute is crucial for a rented infrastructure, which is paid usually on both workload and storage. 
\subsection{Always On}
The very first handicap coming with Che is the requirement for a good internet connection. 
While a common office is already equipped with internet, one may want to work on a train or there is simply a problem with the WiFi in the hotel.
With the possibility to setup Che on localhost, the basics and routines can be learned offline. As the main benefits come in terms of teamwork, this is not a real solution.
\subsection{Knowledge Required}
The primary problem with Che is the requirement for an already dense knowledge of cloud related technology.
Setting up the Workspace, docker-images, build and CI scripts is a complex topic and can not be done by someone getting started. 
This requirement extends when working with a multi-pod-environment. 
While most of the tasks are by themselves rather simple, the bare amount of such tasks (especially when migrating an existing project to Che) requires a broad knowledge.
This can be done by a single expert user, enabling the other developers  to  use  the  build-routines and  environments provided. 
However, many problems which arise are related to the cloud-environment and will be hard to solve by a novice user, making him dependent on the expert. 
It's therefore necessary to get everyone on a certain base-level to solve their own problems, otherwise the expert will be overloaded and the project stuck.

@@

\section{Benefits for Education}
\label{sec:EvalEdu}
In addition to the previous mentioned benefits, there are more points about Che that are especially important for educational purposes, such as courses in the university, professional school or research departments.
For simplicity only universities will be addressed.
\subsection{New motivational and intuitive Courses}
Eclipse Che provides the possibility to learn primary cloud-technologies hands on and in a simple and supportive manner. 
Unfortunately, these topics are currently not widely teached at university.
Che makes it possible to teach students fundamentals of modern software development.
Depending on the courses subject, one can either provide scalable software or a running environment. 
With fitting material provided, it's easy to learn cloud native development, DevOps or Cloud-Operations. 
Even complicated topics, such as micro-services and IoT-applications can easily be adapted inside Che \cite{IV18} and performed as for example as group-projects with a common goal. 
The student will need to understand cloud-components as well as team-work to succeed with Che.

The produced artifacts can simply be shipped as containers, giving comfortable access to the professor. 
With both the product and the code inside the workspace easily accessible, the professor can grant faster and better feedback for the students, which can have massive impact on learning \cite{HU95}\cite{HU18}.
Additionally, the professor can provide automated end-to-end tests with tools such as Jenkins or TravisCI. 
Given such an environment, the student will immediately get objective feedback, whether their code fulfills the requirements. 
This immediate feedback is a big motivator and has a positive impact on the learning experience \cite{FI05}. 
With a clear reason on the usefulness of the task, the visible progress and the direct impact of personal effort should lead to intrinsic motivation, which studies show to have a strong effect on education \cite{DECI93}.

@@

With Eclipse Che many problems about teaching students these Cloud Skills and reducing the initial scope for learning, are addressed. 
While the impacts on motivation and the actual learning results are only hypothetical, most of the technical requirements are solved by Che.  
As Eclipse Che is cutting edge it whatsoever lacks many quality of life features, has some bugs, and the design is undefined to some extend.

>>>>

\begin{abstract}
Eclipse Che is a open source cloud-based IDE, inheriting the approach of building cloud native software within a 
remote environment. 
Instead of developing on a local machine, a remote development-server is accessed via web-browser 
and the artifacts are compiled into docker-containers.

@@

As Cloud is a central element of modern IT-development, it is strange to see that it is not yet widely teached across 
universities in Germany \footnote{https://www.hochschulkompass.de/studium/studiengangsuche lists currently only 10 german universities with courses on cloud computing, about 30 courses on virtualization }.
There are courses to teach either classic virtualization or docker-basics, but the knowledge of full-stack cloud-platforms and cloud native development is sealed behind corporate doors and conference workshops.
Meanwhile,  the  annual  StackOverflow  developer-survey \cite{SO19} showed, that DevOps-engineers are not only 
among the most wanted and best paid jobs but also tend to be the happiest participants.  
Every student either wants to be happy or to be rich (some want both), making Cloud an interesting topic for their career.

@@

The last component is the Che-administration server. 
In the administration-server workspaces are orchestrated and monitored. 
The authorization is also done at the admin-server and not by every workspace.
The workspaces can be shipped onto multiple separate machines.
The runtimes do not necessarily need to be on the same machines as their workspace. 
Instead of the web-based IDE, a desktop IDE can be connected to the workspace. 
This is done by mounting the workspaces-filesystem in the desktop  IDE. 
This  will grant access to auto-completion and other features, but will miss Che specific helpers the web-IDE offers.
This feature looks to be rather a proof of concept.

A single workspace can contain multiple projects, whereof every project will have its own runtime. 
Projects can either share a versioning control or be separated. 
You can build whole pods in a single workspace with the single containers being the sub-projects. 
You can also compose applications inside the workspace, meaning that the resulting 
container of a project can be the base-image of another project. 
A workspace can be shared among multiple users. 
Both will work on the same remote filesystem, altering files simultaneous. 
Due to changes being transmitted as HTTP-requests, the current implementation when working on the same file is a \textit{last write wins}-policy. 
For version 7 a multi-cursor file-editing will be provided, like it`s common in 
OneDrive-documents. 
This is not to be mixed up with having multiple users work on the same project but on their own workspace. 
The code, and the workspace itself, can commonly be shared with any versioning tool such as Git.
It's mostly dependent on the team which kind of cooperation they prefer.

@@

\subsection{Reproducibility and Maintenance}
The University of Arizona showed \cite{CO16}, that about 50\% of software inspected was not able to build. 
Common reasons are missing, changed or faulty dependencies, leading to the common term of \textit{dependency hell} as well as unclear documentation. 
Experienced programmers are usually able to overcome these issues, given enough time. This continues to be an issue \cite{CL14}, and without a different approach probably always will be.

@@

This is one of the primary goals of the DevOps approach \cite{JA16}. 
The workspace can therefore form totally new ways of programming, such as IoT Applications \footnote{the Plugin Arktik for Eclipse offered IoT Development with Che. While Arktik is unsupported since February 2019, it proved that the concept worked.} or a full setup of micro-services \cite{IV18}, while being agile and reproducible.
\subsection{Sharing Results}
The topic \textit{docker for reproducible research} has already been promoted \cite{BO15} and successfully applied to complex topics \cite{ST16} such as machine learning. 
As Clark et al. \cite{CL14} have used code of several repositories provided from their university, most of the projects can be expected scientific or experimental, therefore 50\% of the research results were not reproducible.

@@

The combination of a quick setup and the usability of every enhancement makes Che especially interesting to recruit troubleshooters into projects, which solve some of the very specialized tasks.  
With  the  artifacts  being  reproducible,  the  expert  can quickly inspect the subject and analyze problems.
With a finished workspace they can quickly start working. 
With their changes being also in docker, they will be visible and functional for the whole team.
Therefore,  the  hardest  common  problems  regarding \textit{quick help} are addressed and solved. 
As an additional minor benefit, it is easy to hibernate resources  using  Che  with  Kubernetes  or  Openshift.
The workspaces collect metrics like any other container and are therefore scalable on demand. 
The ability of down-scaling the development resources has a big impact on the overall 
workload. 
As a further example, the workspace could be shut down out of normal business-time. This attribute is crucial for a rented infrastructure, which is paid usually on both workload and storage. 
\subsection{Always On}
The very first drawback coming with Che is the requirement for a good internet connection. 
While a common office is already equipped with internet, one may want to work on a train or there is simply a problem with the WiFi in the hotel.
With the possibility to setup Che on localhost, the basics and routines can be learned offline. As the main benefits come in terms of teamwork, this is not a real solution.
\subsection{Knowledge Required}
The primary problem with Che is the requirement for an already dense knowledge of cloud related technology.
Setting up the Workspace, docker-images, build and CI scripts is a complex topic and can not be done by someone getting started. 
This requirement extends when working with a multi-pod-environment. 
While most of the tasks are by themselves rather simple, the bare amount of such tasks (especially when migrating an existing project to Che) requires a broad knowledge.
This can be done by a single expert user, enabling the other developers  to  use  the  build-routines and  environments provided. 
However, many problems which arise are related to the cloud-environment and will be hard to solve by a novice user, making him dependent on the expert. 
It's therefore necessary to get everyone on a certain base-level to solve their own problems, otherwise the expert will be overloaded and the project stuck.

@@

\section{Benefits for Education}
\label{sec:EvalEdu}
In addition to the previous mentioned benefits, there are more points about Che that are especially important for educational purposes, such as courses in the university, professional school or research departments.
For simplicity only universities will be addressed.
\subsection{New motivational and intuitive Courses}
Eclipse Che provides the possibility to learn primary cloud-technologies hands on and in a simple and supportive manner. 
Unfortunately, these topics are currently not widely teached at university.
Che makes it possible to teach students fundamentals of modern software development.
Depending on the courses subject, one can either provide scalable software or a running environment. 
With suitable material provided, it's easy to learn cloud native development, DevOps or Cloud-Operations. 
Even complicated topics, such as micro-services and IoT-applications can easily be adapted inside Che \cite{IV18} and performed as for example as group-projects with a common goal. 
The student will need to understand cloud-components as well as team-work to succeed with Che.

The produced artifacts can simply be shipped as containers, giving comfortable access to the teaching staff. 
With both the product and the code inside the workspace easily accessible, the teaching staff can grant faster and better feedback for the students, which can have massive impact on learning \cite{HU95}\cite{HU18}.
Additionally, the teacher can provide automated end-to-end tests with tools such as Jenkins or TravisCI. 
Given such an environment, the student will immediately get objective feedback, whether their code fulfills the requirements. 
This immediate feedback is a big motivator and has a positive impact on the learning experience \cite{FI05}. 
With a clear reason on the usefulness of the task, the visible progress and the direct impact of personal effort should lead to intrinsic motivation, which studies show to have a strong effect on education \cite{DECI93}.

@@

With Eclipse Che many problems about teaching students these Cloud Skills and reducing the initial scope for learning, are addressed. 
While the impacts on motivation and the actual learning results are only hypothetical, most of the technical requirements are solved by Che.  
As Eclipse Che is cutting edge it whatsoever lacks many quality of life features, has some bugs, and the preferred design is undefined to some extend.
